LSOA domestic Electricty and Gas maps

### 2021-09-03 LSOA Fuel poverty.Rmd
Graphing the chnage in gas usage against deprevation score

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Over 65 annd Fuel Poverty
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
head(census_age)
names(census_age)
```
```{r Plotting the fuel poverty in over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
Census_age_fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
names(Census_age_fp)
# select the variables we want for clarity
df <- dplyr::select(Census_age_fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65")

>>>>

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Over 65 and Fuel Poverty
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
head(census_age)
names(census_age)
```
```{r Plotting the fuel poverty in over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
Census_age_fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
names(Census_age_fp)
# select the variables we want for clarity
df <- dplyr::select(Census_age_fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65")

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
Graph finished
Graphing the chnage in gas usage against deprevation score

####Map with Overlay 
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)

@@

```{r Mapping the change in LSOA dom mean gas comsumption}
merged_dgas$LSOA11CD <- merged_dgas$"Lower Layer Super Output Area (LSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
ggplot2::ggplot(lsoa_dgas20102019) + geom_sf(aes(fill=dg_diff))+ 
                  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)") ##BROKEN
##Need to change the varibale names to reflect what is actually there
```
####Map with overlay 
```{r Check leaflet for change i dom gas consumption}
library(leaflet)

>>>>

nrow(Solent)
```
####Map with Overlay 
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)

@@

```{r Mapping the change in LSOA dom mean gas comsumption}
merged_dgas$LSOA11CD <- merged_dgas$"Lower Layer Super Output Area (LSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
ggplot2::ggplot(lsoa_dgas20102019) + geom_sf(aes(fill=dg_diff))+ 
                  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)") ##BROKEN
##Need to change the varibale names to reflect what is actually there

lsoa_dgas20102019$pc_diff <- 100*(lsoa_dgas20102019$dg_diff/lsoa_dgas20102019$dgas2010)
t_diff <-  dplyr::select(as.data.frame(lsoa_dgas20102019), 
                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Code`,
                         dgas2010, dgas2019, dg_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
  geom_histogram()

```
####Plotting the change in gas usage against the deprevation 
```{r plotting change in gas usage against dep}
LSOAdepgas <- merge(merged_dgas, LSOAdep, by= "LSOA11CD")
names(LSOAdepgas)
df <- dplyr::select(LSOAdepgas, LSOA11CD, "Local Authority Name.x", dg_diff, IMDScore, dgas2010, IMD_Decile
)

head(df)
Solent <- dplyr::filter(df, `Local Authority Name.x` == "Basingstoke and Deane"|
                           `Local Authority Name.x` == "East Hampshire"|
                           `Local Authority Name.x` == "Eastleigh"|
                           `Local Authority Name.x` == "Fareham"|
                           `Local Authority Name.x` == "Gosport"|
                           `Local Authority Name.x` == "Hart"|
                           `Local Authority Name.x` == "Havant"|
                           `Local Authority Name.x` == "New Forest"|
                           `Local Authority Name.x` == "Portsmouth"|
                           `Local Authority Name.x` == "Rushmoor"|
                           `Local Authority Name.x` == "Southampton"|
                           `Local Authority Name.x` == "Test Valley"|
                           `Local Authority Name.x` == "Winchester"|
                           `Local Authority Name.x` == "Isle of Wight"
                           )
head(Solent)
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/dgas2010), 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "% change")
```

```{r addFacetsToElecDiff}
# or without colour but using facets for Local Authorities
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/dgas2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change") +
  facet_wrap(`Local Authority Name.x` ~ .)

####Map with overlay 
```{r Check leaflet for change i dom gas consumption}
library(leaflet)
